Simple models of deliberated preference

### 2018-01-29 simple.tex
Finished refactor with \phi

We can now define $\iPhi \subseteq \Phi$: $\phi \in \iPhi ⇔  \exists \ar \ \phi\text{-dec}$.
\footnote{Equivalently: $\iPhi = \bigcup_{\ar \in \allargs} \bigcap{\ar' \in \allargs} \ileadstost(\ar', \ar)$.}
\footnote{$\phi \in \iPhi ⇔ \exists \ar \suchthat \allargs × \{\ar\} \ileadstost \phi$.}
\footnote{\label{ft:notposs}$\prop \in \iposs ⇔ \exists \ar \ \proppossdec$ and $\prop \notin \iposs ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstose ¬\prop$.}
\footnote{\label{ft:notsure}$\prop \in \isure ⇔ \exists \ar \ \propsuredec$ and $¬\prop \notin \isure ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstope \prop$.}

@@

Given a decision situation, we define the relations $\wibeatse[\prop], \nwibeatse[¬\prop] \subseteq \mbeats$ in order to obtain the following result.

Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \wibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$.
\footnote{Or $\ar_2 \ileadsto \prop ∧ ¬\prop \notin \mleadsto(\allargs) ∧ (\ar_3, \ar_2) \ileadstope ¬\prop$.}

Given $\ar_3 \mbeats \ar_2, \prop \in \alltopic$: $\ar_3 \nwibeatse[\prop] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstope \prop]$.

This is done with the following construction.
Given a model. 
\begin{itemize}
	\item Define a root as an argument that $\mbeats$-attacks nothing. 
	\item Associate to each $\ar \in \clargs$ its depth $d(\ar)$, the distance to the farthest root: $d(\ar) = 0$ iff $\ar$ is a root and $d(\ar) = k+1$ iff $\ar$ $\mbeats$-attacks some $\ar'$ of depth $k$ and $\mbeats$-attacks no $\ar'$ of depth superior to $k$. \footnote{Thus $d(\ar) = 1$ iff $\ar$ attacks some and only root nodes; $d(\ar) = 2$ iff $\ar$ attacks some node of depth 1 and only nodes of depth 1 or 0; and so on.} 
	\item Observe that if $\ar_3 \mbeats \ar_2$ and $d(\ar_3) = k+1$, then $d(\ar_2) ≤ k$. 
	\item Define $\wibeatse[\prop]_{(0)} = \nwibeatse[\prop]_{(0)} = \emptyset$. 
	\item Define $\wibeatse[\prop]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\prop]_{(k+1)} \ar_2$ iff $\ar_3 \mbeats \ar_2$, $d(\ar_3) = k+1$, and: $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\prop]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\prop]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \prop ∧ (\ar_3, \ar_2) \ileadstose ¬\prop]$. Proceed similarly for $\nwibeatse[\prop]_{(k+1)}$.
	\item Define $\wibeatse[\prop] = \bigcup_{k ≥ 0} \wibeatse[\prop]_{(k)}$, and similarly for $\nwibeatse[\prop]$.
\end{itemize}

{Check: Given $\ar_4 \mbeats \ar_3, \ar_3 \notin \mleadstoinv(\alltopic)$, with $\ar_2 \in \mbeats(\ar_3)$ ⇒ ($\ar_2$ and $\ar_4 + \ar_2$ $\mbeats$-attack only root nodes and do not support any proposition): $\ar_4 \wibeatse[\prop] \ar_3$ iff
\begin{itemize}
	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\ar_3 \wibeatse[\prop] \ar_2) ∧ (\ar_3 \nwibeatse[\prop] \ar_4 + \ar_2)]$ iff 
	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_2 \nwibeatse[\prop] \ar_3 + \ar_1) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_4 + \ar_2 \wibeatse[\prop] \ar_1 ∧ \ar_4 + \ar_2 \wibeatse[\prop] \ar_3 + \ar_1)]$ iff 
	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_1 \ileadsto t ∧ (\ar_2, \ar_1) \ileadstose ¬\prop ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ (\ar_3 + \ar_1, \ar_2) \ileadstope \prop ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_1 \mleadsto \prop ∧ (\ar_4 + \ar_2, \ar_1) \ileadstose ¬\prop ∧ \ar_3 + \ar_1 \ileadsto \prop ∧ (\ar_4 + \ar_2, \ar_3 + \ar_1) \ileadstose ¬\prop)]$.
\end{itemize}
}

Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\prop] \ar_1$, we have: $\ar_3 \wibeatse[\prop] \ar_2 ∨ \ar_3 \nwibeatse[\prop] \ar_2$.

Define $\ar_2 \wibeatse \ar_1 ⇔ \exists \prop \in \alltopic \suchthat \ar_2 \wibeatse[\prop] \ar_1$.

@@

Define $\argsdec^\prop = \clargs \setminus \text{im}(\wibeatse[\prop])$ the decisive arguments according to $\wibeatse[\prop]$, or $\wibeatse[\prop]$-decisive arguments for short: $\ar \in \argsdec ⇔ \wibeatseinv[\prop](\ar) = \emptyset$.

\begin{definition}[Reinstatement]
	Given $\ar_3 \wibeatse[\prop] \ar_2 \wibeatse[\prop] \ar_1, \ar_3 \in \argsdec^\prop$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive. This should not invalidate the conditions, but it does currently. But it’s not a problem: the model would actually not be built this way. In this scenario the argument $\ar_3 + \ar_1$ is useful only in case $\ar_3$ is decisive, thus $\ar_4 \mbeats \ar_3 + \ar_1$ must not be planned. Rather $\ar_5 + \ar_3$ decisive, then $(\ar_5 + \ar_3) + \ar_1$. Alternatively, also $\ar_4 \mbeats \ar_1$ and then no problem as well.}
	\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
	\footnote{We do not mandate that $\ar_3 + \ar_1 \ileadsto \prop$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice). We need: Obs applies to restricted supports (one per prop decided by model); Covering applies to extended supports (restricted supports plus those obtained by reinstatement). Replacement-1 applies to all and requires attack at least as large; Replacement-2 applies to restricted supports and requires no new $\ibeatse$-attacks.}
	\footnote{Is Reinf equivalent to Justifiable unstability? Define $\ar_3 \wibeatsst[\prop] \ar_2 ⇔ \ar_3 \wibeatse[\prop] \ar_2 ∧ ¬(\ar_3 \nwibeatse[\prop] \ar_2)$. Prove that $\ar_3 \wibeatsst[\prop] \ar_2 \wibeatse[\prop] \ar_2 ⇒ ¬(\ar_2 \wibeatse[\prop] \ar_3 + \ar_1)$.} 
\end{definition}

\begin{definition}[Justifiable unstability]
	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse[\prop] \ar_1, \ar_2 \nwibeatse[\prop] \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$.
\end{definition}

$\ar$ is $\prop$-defended iff $\wibeatseinv[\prop](\ar) \subseteq \wibeatse[\prop](\argsdec^\prop)$ (its $\wibeatse$-attackers are $\wibeatse$-attacked by $\wibeatse$-decisive arguments).

\begin{definition}[Finite defense]
	If $\wibeatseinv[\prop](\ar) \subseteq \wibeatse[\prop](\argsdec^\prop)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse[\prop](\args)$.
\footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check). But it may be interesting to not limit it and declare that the model has specific replies to any counter-argument, but promises to use only a few rebuttals and that afterwards, the dm will stop using those kind of arguments (but we don’t know in advance which ones will be chosen).}
\end{definition}
Thus, if the attackers of $\ar$ are attacked by decisive arguments, then $j$ defenders are enough to defend $\ar$.

Define $R^\prop$, the reinstates relation, as follows: $(\ar_3 + \ar_1) R^\prop \ar_1$ iff $\ar_3 \wibeatse[\prop] \ar_2 \wibeatse[\prop] \ar_1$ (for some $\ar_2, \prop$), $\ar_3 \in \argsdec^\prop$. Define $\gdargs^\prop$ as the transitive closure of $\mleadstoinv(\alltopic)$ under $R^\prop$. Given $\prop, \ar \in \gdargs^\prop, \ar' \in \allargs$, define $\ar' \ibeatse[\prop] \ar ⇔ (\ar', \ar) \ileadstose ¬\prop$.
\begin{definition}[Covering]
	$\forall \prop, \ar \in \gdargs^\prop, \ar' \in \allargs: \ar' \ibeatse[\prop] \ar ⇒ \ar' \mbeats \ar$. 
\end{definition}

\begin{definition}[Observable validity]
	$\forall \ar_2 \mbeats \ar_1 \mleadsto \prop: ¬(\ar_2 \wibeatse[\prop] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\prop] \ar_2$. Furthermore, if $¬(\clargs \mleadsto \prop), \forall \ar_1 \mleadsto ¬\prop, \ar \in \allargs: (\ar_1, \ar) \ileadstose ¬\prop$.
	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits). Thus we only need to prove $\prop \notin \iposs$, for which $(\ar_1, \ar) \ileadstose ¬\prop$ suffices.}
\end{definition}

\section{Theorem}
\begin{theorem}[Validity]
	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iposs$. Furthermore, if $¬\prop \in \mleadsto(\clargs) ∧ \prop \notin \mleadstoinv(\clargs)$, $¬\prop \in \isure$.
\end{theorem}
\begin{proof}
First, we want to prove that $\ar_1$ $\prop$-defended implies $\ar_1$ replaceable by some $\wibeatse[\prop]$-decisive $\ar$, and if $\ar_1 \in \gdargs$, then its replacer $\ar$ is in $\gdargs$ as well.

Because $\ar_1$ is $\prop$-defended, $\exists \args \subseteq \argsdec^\prop \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse[\prop](\args)$, $\args$ finite [Finite defense].

Pick any $\ar_{3, 1} \in \args$ such that $\ar_{3, 1} \wibeatse \ar_2 \wibeatse \ar_1$ (if there’s none, $\ar_1 \in \argsdec$ and we’re done). $\ar_{3, 1} + \ar_1$ replaces $\ar_1$, and $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_{3, 1})$ [Reinstatement]. Hence, $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \wibeatse[\prop](\args) \setminus \mbeats(\ar_{3, 1})$. Iterate by picking any $\ar_{3, 2} \in \args$ such that $\ar_{3, 2} \wibeatse \ar_2 \wibeatse \ar_{3, 1} + \ar_1$ (if there’s none, $\ar_{3, 1} + \ar_1 \in \argsdec$ and we’re done) and obtaining $\ar_{3, 2} + (\ar_{3, 1} + \ar_1)$ replacing $\ar_{3, 1} + \ar_1$ (hence, replacing $\ar_1$) with $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \mbeatsinv(\ar_{3, 1} + \ar_1) \setminus \mbeats(\ar_{3, 2})$. Hence, $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \wibeatse[\prop](\args) \setminus \mbeats(\ar_{3, 1}) \setminus \mbeats(\ar_{3, 2})$. Iterating in such a way over the finite set $\args$ will finally yield an element that is $\wibeatse[\prop]$-decisive. The last point, $\ar_1 \in \gdargs ⇒ \ar \in \gdargs$, follows from the definition of $\gdargs$.

Second, we want to prove that if $\ar_1$ is not $\prop$-defended and has no decisive $\wibeatse[\prop]$-attackers (meaning that $\wibeatseinv[\prop](\ar_1) \subseteq \overline{\argsdec^\prop}$), then $\ar_1$ is $\wibeatse[\prop]$-attacked by some $\ar_2$ that is not $\prop$-defended and has no decisive $\wibeatse[\prop]$-attacker.

Consider $\ar_1$ not $\prop$-defended and having no decisive $\wibeatse[\prop]$-attackers. Because $\ar_1$ is not $\prop$-defended, by definition, it is $\wibeatse[\prop]$-attacked by some $\ar_2$ that has no decisive $\wibeatse[\prop]$-attacker. Because $\ar_1$ has no decisive attacker, $\ar_2$ is not decisive. If $\ar_2$ was defended, by the first part of this proof, it would be replaceable by a decisive argument, and $\ar_1$ would have a decisive attacker. Thus, $\ar_2$ is not defended.

We conclude from this second point that if $\wibeatseinv[\prop](\ar_1) \subseteq \overline{\argsdec^\prop}$, then $\ar_1$ is $\prop$-defended. Otherwise, it is attacked by some $\ar_2$, on which the condition applies in turn, thus attacked by some $\ar_3$, on which the condition applies, and iterating in this way and using finiteness of $\wibeatse[\prop]$ leads to a contradiction.

Third, consider an argument $\ar_1 \in \mleadstoinv(\alltopic)$. If some $\ar_2 \wibeatse[\prop] \ar_1$ then $\ar_3 \wibeatse[\prop] \ar_2$ [Obs val]. Thus, $\wibeatseinv[\prop](\ar_1) \subseteq \overline{\argsdec^\prop}$. Thus, $\ar_1$ is $\prop$-defended, by our second point. Hence, by our first point in this proof, $\ar_1$ is replaceable by some $\wibeatse[\prop]$-decisive $\ar \in \gdargs$. We obtain that $\forall \ar' \in \allargs: ¬(\ar' \wibeatse[\prop] \ar)$. As $\ar \in \gdargs$, $\ar' \ibeatse[\prop] \ar ⇒ \ar' \wibeatse[\prop] \ar$ [Covering], thus we obtain $¬(\ar' \ibeatse[\prop] \ar)$, hence $\ar$ is $\prop$-poss-dec and $\prop \in \iposs$.
\end{proof}

>>>>

We can now define $\iPhi \subseteq \Phi$: $\phi \in \iPhi ⇔  \exists \ar \ \phi\text{-dec}$.
\footnote{Equivalently: $\iPhi = \bigcup_{\ar \in \allargs} \bigcap_{\ar' \in \allargs} \ileadstost(\ar', \ar)$.}
\footnote{$\phi \in \iPhi ⇔ \exists \ar \suchthat \allargs × \{\ar\} \ileadstost \phi$.}
\footnote{\label{ft:notposs}$\prop \in \iposs ⇔ \exists \ar \ \proppossdec$ and $\prop \notin \iposs ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstose ¬\prop$.}
\footnote{\label{ft:notsure}$\prop \in \isure ⇔ \exists \ar \ \propsuredec$ and $¬\prop \notin \isure ⇔ \forall \ar, \exists \ar' \suchthat (\ar', \ar) \ileadstope \prop$.}

@@

Given a decision situation, we define the relations $\wibeatse[\phi], \nwibeatse[¬\phi] \subseteq \mbeats$ in order to obtain the following result.

Given $\ar_3 \mbeats \ar_2, \phi \in \Phi$: $\ar_3 \wibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \nwibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe ¬\phi]$.

Given $\ar_3 \mbeats \ar_2, \phi \in \iPhi$: $\ar_3 \nwibeatse[\phi] \ar_2$ iff $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \wibeatse[\phi] \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe \phi]$.

This is done with the following construction.
Given a model. 
\begin{itemize}
	\item Define a root as an argument that $\mbeats$-attacks nothing. 
	\item Associate to each $\ar \in \clargs$ its depth $d(\ar)$, the distance to the farthest root: $d(\ar) = 0$ iff $\ar$ is a root and $d(\ar) = k+1$ iff $\ar$ $\mbeats$-attacks some $\ar'$ of depth $k$ and $\mbeats$-attacks no $\ar'$ of depth superior to $k$. \footnote{Thus $d(\ar) = 1$ iff $\ar$ attacks some and only root nodes; $d(\ar) = 2$ iff $\ar$ attacks some node of depth 1 and only nodes of depth 1 or 0; and so on.} 
	\item Observe that if $\ar_3 \mbeats \ar_2$ and $d(\ar_3) = k+1$, then $d(\ar_2) ≤ k$. 
	\item Define $\wibeatse[\phi]_{(0)} = \nwibeatse[\phi]_{(0)} = \emptyset$. 
	\item Define $\wibeatse[\phi]_{(k+1)} \subseteq \mbeats$, $k ≥ 0$, as $\ar_3 \wibeatse[\phi]_{(k+1)} \ar_2$ iff $\ar_3 \mbeats \ar_2$, $d(\ar_3) = k+1$, and: $[\exists \ar_1 \in \mbeats(\ar_2) \suchthat (\ar_2 \wibeatse[\phi]_{(d(\ar_2))} \ar_1 ∧ \ar_2 \nwibeatse[\phi]_{(d(\ar_2))} \ar_3 + \ar_1)] ∨ [\ar_2 \mleadsto \phi ∧ (\ar_3, \ar_2) \ileadstoe ¬\phi]$. Proceed similarly for $\nwibeatse[\phi]_{(k+1)}$.
	\item Define $\wibeatse[\phi] = \bigcup_{k ≥ 0} \wibeatse[\phi]_{(k)}$, and similarly for $\nwibeatse[\phi]$.
\end{itemize}

{Check: Given $\ar_4 \mbeats \ar_3, \ar_3 \notin \mleadstoinv(\alltopic)$, with $\ar_2 \in \mbeats(\ar_3)$ ⇒ ($\ar_2$ and $\ar_4 + \ar_2$ $\mbeats$-attack only root nodes and do not support any proposition): $\ar_4 \wibeatse[\phi] \ar_3$ iff
\begin{itemize}
	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\ar_3 \wibeatse[\phi] \ar_2) ∧ (\ar_3 \nwibeatse[\phi] \ar_4 + \ar_2)]$ iff 
	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_2 \nwibeatse[\phi] \ar_3 + \ar_1) ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_4 + \ar_2 \wibeatse[\phi] \ar_1 ∧ \ar_4 + \ar_2 \wibeatse[\phi] \ar_3 + \ar_1)]$ iff 
	\item $\exists \ar_2 \in \mbeats(\ar_3) \suchthat [(\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_1 \ileadsto t ∧ (\ar_2, \ar_1) \ileadstose ¬\phi ∧ \ar_3 + \ar_1 \ileadsto \phi ∧ (\ar_3 + \ar_1, \ar_2) \ileadstope \phi ∧ (\exists \ar_1 \in \mbeats(\ar_4 + \ar_2) \suchthat \ar_1 \mleadsto \phi ∧ (\ar_4 + \ar_2, \ar_1) \ileadstose ¬\phi ∧ \ar_3 + \ar_1 \ileadsto \phi ∧ (\ar_4 + \ar_2, \ar_3 + \ar_1) \ileadstose ¬\phi)]$.
\end{itemize}
}

Given $\ar_3 \in \clargs, \ar_2 \in \clargs$, with $\exists \ar_1 \in \mbeats(\ar_2) \suchthat \ar_2 \wibeatse[\phi] \ar_1$, we have: $\ar_3 \wibeatse[\phi] \ar_2 ∨ \ar_3 \nwibeatse[\phi] \ar_2$.

Define $\ar_2 \wibeatse \ar_1 ⇔ \exists \phi \in \alltopic \suchthat \ar_2 \wibeatse[\phi] \ar_1$.

@@

Define $\argsdec^\phi = \clargs \setminus \text{im}(\wibeatse[\phi])$ the decisive arguments according to $\wibeatse[\phi]$, or $\wibeatse[\phi]$-decisive arguments for short: $\ar \in \argsdec^\phi ⇔ \wibeatseinv[\phi](\ar) = \emptyset$.

We say that $\ar$ replaces $\ar_1$ iff $\mbeats(\ar_1) \subseteq \mbeats(\ar)$.

\begin{definition}[Reinstatement]
	Given $\ar_3 \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1, \ar_3 \in \argsdec^\phi$: $\mbeats(\ar_1) \subseteq \mbeats(\ar_3 + \ar_1)  ∧ \mbeatsinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$.
	\footnote{TODO the condition must be $\wibeatseinv(\ar_3 + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_3)$ to allow $\ar_5 \mbeats \ar_4 \mbeats \ar_3 \mbeats \ar_2 \mbeats \ar_1$ and $\ar_5 \mbeats \ar_4 \mbeats \ar_3 + \ar_1$, considering that possibly $\ar_3$ is $\wibeatse$-decisive. This should not invalidate the conditions, but it does currently. But it’s not a problem: the model would actually not be built this way. In this scenario the argument $\ar_3 + \ar_1$ is useful only in case $\ar_3$ is decisive, thus $\ar_4 \mbeats \ar_3 + \ar_1$ must not be planned. Rather $\ar_5 + \ar_3$ decisive, then $(\ar_5 + \ar_3) + \ar_1$. Alternatively, also $\ar_4 \mbeats \ar_1$ and then no problem as well.}
	\footnote{The stronger condition mandating $\mbeatsinv(\ar_3 + \ar_1) \subseteq \wibeatseinv(\ar_1) \setminus \mbeats(\ar_3)$ would be more difficult to check: when some $\ar_2 \wibeatse \ar_3 + \ar_1$, we’d need to check not only that $\ar_2 \mbeats \ar_1$ but also $\ar_2 \wibeatse \ar_1$.}
	\footnote{We do not mandate that $\ar_3 + \ar_1 \ileadsto \phi$, so that the model can afford not resisting to the counter-attacks to $\ar_3 + \ar_1$ (resistance to c-a to $\ar_1$ suffice).}
	\footnote{Is Reinf equivalent to Justifiable unstability? Define $\ar_3 \wibeatsst[\phi] \ar_2 ⇔ \ar_3 \wibeatse[\phi] \ar_2 ∧ ¬(\ar_3 \nwibeatse[\phi] \ar_2)$. Prove that $\ar_3 \wibeatsst[\phi] \ar_2 \wibeatse[\phi] \ar_2 ⇒ ¬(\ar_2 \wibeatse[\phi] \ar_3 + \ar_1)$.} 
\end{definition}

\begin{definition}[Justifiable unstability]
	$\forall \ar_2 \mbeats \ar_1 \suchthat \ar_2 \wibeatse[\phi] \ar_1, \ar_2 \nwibeatse[\phi] \ar_1: \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\phi] \ar_2$.
\end{definition}

$\ar$ is $\phi$-defended iff $\wibeatseinv[\phi](\ar) \subseteq \wibeatse[\phi](\argsdec^\phi)$ (its $\wibeatse[\phi]$-attackers are $\wibeatse[\phi]$-attacked by $\wibeatse[\phi]$-decisive arguments).

\begin{definition}[Finite defense]
	If $\wibeatseinv[\phi](\ar) \subseteq \wibeatse[\phi](\argsdec^\phi)$, then $\exists \args \subseteq \argsdec, \card{\args} ≤ j \suchthat \mbeatsinv(\ar) \subseteq \wibeatse[\phi](\args)$.
\footnote{To satisfy Finite defense, in presence of the other conditions, suffice to limit the width of the model (TODO check). But it may be interesting to not limit it and declare that the model has specific replies to any counter-argument, but promises to use only a few rebuttals and that afterwards, the dm will stop using those kind of arguments (but we don’t know in advance which ones will be chosen).}
\end{definition}
Thus, if the attackers of $\ar$ are attacked by decisive arguments, then $j$ defenders are enough to defend $\ar$.

Define $R^\phi$, the reinstates relation, as follows: $(\ar_3 + \ar_1) R^\phi \ar_1$ iff $\ar_3 \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1$ (for some $\ar_2, \phi$), $\ar_3 \in \argsdec^\phi$. Define $\gdargs^\phi$ as the transitive closure of $\mleadstoinv(\Phi)$ under $R^\phi$. Given $\phi, \ar \in \gdargs^\phi, \ar' \in \allargs$, define $\ar' \ibeatse[\phi] \ar ⇔ (\ar', \ar) \ileadstoe ¬\phi$.
\begin{definition}[Covering]
	$\forall \phi, \ar \in \gdargs^\phi, \ar' \in \allargs: \ar' \ibeatse[\phi] \ar ⇒ \ar' \mbeats \ar$. 
\end{definition}

\begin{definition}[Observable validity]
	$\forall \ar_2 \mbeats \ar_1 \mleadsto \phi: ¬(\ar_2 \wibeatse[\phi] \ar_1) ∨ \exists \ar_3 \mbeats \ar_2 \suchthat \ar_3 \wibeatse[\phi] \ar_2$.
	\footnote{If the model claims $¬\prop \in \isure$, this requires clear-cut (for that prop), so we must mandate it (hopefully A3 or an equivalent such as Justifiable unstability fits). Thus we only need to prove $\prop \notin \iposs$, for which $(\ar_1, \ar) \ileadstose ¬\prop$, for each $\ar$, suffices. In fact, from $\ar_1$ in the model arguing for $\phi$ and $(\ar_1, \ar) \ileadstoe \phi \forall \ar \in \allargs$, we should probably be able, using the argument in the theorem about finite chains, to deduce that this is enough to conclude that $\ar_1$ is $\phidec$.}
\end{definition}

\section{Theorem}
\begin{theorem}[Validity]
	Given a decision situation and a model $\eta$, if all our conditions are satisfied, $\mleadsto(\clargs) \subseteq \iPhi$.
\end{theorem}
\begin{proof}
First, we want to prove that $\ar_1$ $\phi$-defended implies $\ar_1$ replaceable by some $\wibeatse[\phi]$-decisive $\ar$, and if $\ar_1 \in \gdargs^\phi$, then its replacer $\ar$ is in $\gdargs^\phi$ as well.

Because $\ar_1$ is $\phi$-defended, $\exists \args \subseteq \argsdec^\phi \suchthat \mbeatsinv(\ar_1) \subseteq \wibeatse[\phi](\args)$, $\args$ finite [Finite defense].

Pick any $\ar_{3, 1} \in \args$ such that $\ar_{3, 1} \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_1$ (if there’s none, $\ar_1 \in \argsdec^\phi$ and we’re done). $\ar_{3, 1} + \ar_1$ replaces $\ar_1$, and $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \mbeatsinv(\ar_1) \setminus \mbeats(\ar_{3, 1})$ [Reinstatement]. Hence, $\mbeatsinv(\ar_{3, 1} + \ar_1) \subseteq \wibeatse[\phi](\args) \setminus \mbeats(\ar_{3, 1})$. Iterate by picking any $\ar_{3, 2} \in \args$ such that $\ar_{3, 2} \wibeatse[\phi] \ar_2 \wibeatse[\phi] \ar_{3, 1} + \ar_1$ (if there’s none, $\ar_{3, 1} + \ar_1 \in \argsdec^\phi$ and we’re done) and obtaining $\ar_{3, 2} + (\ar_{3, 1} + \ar_1)$ replacing $\ar_{3, 1} + \ar_1$ (hence, replacing $\ar_1$) with $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \mbeatsinv(\ar_{3, 1} + \ar_1) \setminus \mbeats(\ar_{3, 2})$. Hence, $\mbeatsinv(\ar_{3, 2} + (\ar_{3, 1} + \ar_1)) \subseteq \wibeatse[\phi](\args) \setminus \mbeats(\ar_{3, 1}) \setminus \mbeats(\ar_{3, 2})$. Iterating in such a way over the finite set $\args$ will finally yield an element that is $\wibeatse[\phi]$-decisive. The last point, $\ar_1 \in \gdargs^\phi ⇒ \ar \in \gdargs^\phi$, follows from the definition of $\gdargs^\phi$.

Second, we want to prove that if $\ar_1$ is not $\phi$-defended and has no decisive $\wibeatse[\phi]$-attackers (meaning that $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$), then $\ar_1$ is $\wibeatse[\phi]$-attacked by some $\ar_2$ that is not $\phi$-defended and has no decisive $\wibeatse[\phi]$-attacker.

Consider $\ar_1$ not $\phi$-defended and having no decisive $\wibeatse[\phi]$-attackers. Because $\ar_1$ is not $\phi$-defended, by definition, it is $\wibeatse[\phi]$-attacked by some $\ar_2$ that has no decisive $\wibeatse[\phi]$-attacker. Because $\ar_1$ has no decisive attacker, $\ar_2$ is not decisive. If $\ar_2$ was defended, by the first part of this proof, it would be replaceable by a decisive argument, and $\ar_1$ would have a decisive attacker. Thus, $\ar_2$ is not defended.

We conclude from this second point that if $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$, then $\ar_1$ is $\phi$-defended. Otherwise, it would be attacked by some $\ar_2$, on which the condition would apply in turn, thus which would be attacked by some $\ar_3$, on which the condition would apply, and iterating in this way would build an infinite chain in $\wibeatse[\phi]$, a contradiction.

Third, consider an argument $\ar_1 \in \mleadstoinv(\Phi)$. If some $\ar_2 \wibeatse[\phi] \ar_1$ then $\ar_3 \wibeatse[\phi] \ar_2$ [Obs val]. Thus, $\wibeatseinv[\phi](\ar_1) \subseteq \overline{\argsdec^\phi}$. Thus, $\ar_1$ is $\phi$-defended, by our second point. Hence, by our first point in this proof, $\ar_1$ is replaceable by some $\wibeatse[\phi]$-decisive $\ar \in \gdargs$. We obtain that $\forall \ar' \in \allargs: ¬(\ar' \wibeatse[\phi] \ar)$. As $\ar \in \gdargs$, $\ar' \ibeatse[\phi] \ar ⇒ \ar' \wibeatse[\phi] \ar$ [Covering], thus we obtain $¬(\ar' \ibeatse[\phi] \ar)$, hence $\ar$ is $\phidec$ and $\phi \in \iPhi$.
\end{proof}
